Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-05-01 Ben_Manuscripts/transport/Draft.tex
Updated TOC image
Finalized TOC image
Addressing Doug's comments on conclusions

  We learned that the MSD of solutes, water and counter ions are highly 
  dependent on LLC membrane water content. The MSD of these components is about
  2 orders of magnitude larger in the 10 wt\% system than in the 5 wt\% system.
  As more water is added to the system, the pores become less crowded with monomer
  components. The amount of water in the pores deserves special attention when 
  screening new monomers.

  We observed three mechanisms of solute entrapment.
  \begin{enumerate}
    \item Solutes can become entangled among monomer tails. 
    \item Solutes can donate hydrogen bonds to immobile monomers.
    \item Solutes can associate with counterions.
  \end{enumerate}

  The chemical functionality of solutes influences the degree to which
  they are affected by each trapping mechanism. Simple alcohols tend to
  partition into the tail region as their hydrophobic tail increases in length.
  Alcohols and sugars with multiple hydroxyl groups are very stable
  in the pore region, but frequent hydrogen bonds with monomer head 
  groups prevents them from diffusing quickly. This effect is reduced when
  hydroxyl groups are replaced with thiol groups but the solutes become less
  stable in the pore. Finally, solutes with carbonyl groups, which includes
  the ketones, amides and solutes that can only accept hydrogen bonds, associate
  with sodium ions, temporarily slowing or immobilizing them.

  Based on these trapping mechanisms, we can suggest modifications that
  can be made to monomers in order to mitigate or enhance their effect on
  solute MSDs. Since solutes move slowly while entangled among the monomer
  tails, one can try to design monomers that better control the partition
  of solutes between the pore and tail region. For example, removal of the 
  ether linkages between the head groups and the monomer tails will decrease
  the stability of polar molecules near the head groups. Alternatively, one
  can focus on designing head groups with varying hydrogen bonding capabilities.
  One can increase the number of hydrogen bonding sites on the head groups
  in order to trap more solutes, or decrease the number of hydrogen bond sites
  to trap less. Finally, one can attempt to control the degree to which solutes
  coordinate with counterions. Changing the size and valence of the counter 
  ion may offer some interesting behavior.

  Combined with our previous structural work, it is relatively straightforward
  to apply our approaches to the screening of solute interactions with new 
  H\textsubscript{II} phase-forming monomers.

@@

>>>>

  We learned that the MSD of solutes, water and counter ions are highly 
  dependent on LLC membrane water content. As more water is added to the system, 
  the pores become less crowded with monomer components. The MSDs of water and
  sodium ions are nearly 2 orders of magnitude larger in the 10 wt\% system 
  than in the 5 wt\% system. The amount of water in the pores deserves special
  attention when screening new monomers.

  The transport of polar solutes in this system is significantly slower than
  that of water due to their interaction with the LLC monomers. We observed 
  three primary mechanisms of solute entrapment within the pores.
  \begin{enumerate}
    \item Solutes can become entangled among monomer tails. 
    \item Solutes can donate hydrogen bonds to immobile monomers.
    \item Solutes can associate with counterions.
  \end{enumerate}

  The chemical functionality of solutes influences the degree to which
  they are affected by each trapping mechanism. Simple alcohols tend to
  partition into the tail region as their hydrophobic tail increases in length.
  Alcohols and sugars with multiple hydroxyl groups are very stable
  in the pore region, but frequent hydrogen bonds with monomer head 
  groups prevent them from diffusing quickly. This effect is reduced when
  hydroxyl groups are replaced with thiol groups, but the solutes become less
  stable in the pore. Finally, solutes with carbonyl groups, which includes
  the ketones, amides and solutes that can only accept hydrogen bonds, associate
  with sodium ions, temporarily slowing or immobilizing them.

  Based on these trapping mechanisms, we can suggest modifications that
  can be made to monomers in order to mitigate or enhance their effect on
  solute MSDs. Since solutes move slowly while entangled among the monomer
  tails, one can try to design monomers that better control the partition
  of solutes between the pore and tail region. For example, removal of the 
  ether linkages between the head groups and the monomer tails will decrease
  the stability of polar molecules near the head groups. Alternatively, one
  can focus on designing head groups with varying hydrogen bonding capabilities.
  One can increase the number of hydrogen bonding sites on the head groups
  in order to trap more solutes, or decrease the number of hydrogen bond sites
  to trap less. Finally, one can attempt to control the degree to which solutes
  coordinate with counterions. Changing the size and valence of the counter 
  ion may offer some interesting behavior. These hypotheses remain to be 
  tested in future simulations of new monomers.

  The optimal design of new LLC membranes for a given separation is not obvious.
  Experimental progress up to this point in time is the culmination of an iterative 
  educated guess-and-check framework. An array of solute-membrane interactions
  ensuing from the chemically complex and inhomogeneous LLC membrane structure
  as well as the complexity of the solutes themselves, have hindered the 
  establishment of firm design criteria. Our atomistic modeling approach gives
  us the opportunity to approximate these interactions at the molecular scale
  so that we can observe them and think more critically about LLC membrane design. 
%  We can use insights gained from our model to hypothesize and screen new monomers
%  in order to rapidly increase LLC membrane development.

@@

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=3.25in]{toc_transport.pdf}
  \end{figure}
